---
title: "Metadata"
author: "Wells"
date: "2026-09-15"
output: html_document
---

Class exercise to import your project metadata from the spreadsheet into R 

--Create a folder called "class_project" in your code folder 

--Save this file to the "class_project" folder 

--Move your Nexis spreadsheet to the folder 

--Create a project file on R Studio: File \| New Project \| \*\*\* select Existing folder \| "class_project" 

--After project.Rproj launches, then launch this file, metadata.Rmd, and complete the tutorial

**By doing this, you avoid the ring of hell where R can't find your data**

#load tidyverse, janitor, rio

```{r}

library(tidyverse)
library(janitor)
library(rio)
install.packages("readxl")
library(readxl)

```

#Import your data

```{r}

data <- read_excel("Disinformation_Search_Results")
View(data)

```

# Clean names

```{r}
data <- data |> 
  clean_names()

```

# check data types
```{r}
glimpse(data)
```


Next Steps: Count years, and create a ggplot

# Transform date into years. See tutorial
```{r}

data <- data |> 
  mutate(year = year(published_date))

```


# Create a ggplot
```{r}
company_counts <- data |>
  filter(!is.na(company)) |>
  mutate(company = case_when(
    company %in% c("FACEBOOK INC", "META PLATFORMS INC") ~ "META (FACEBOOK)",
    TRUE ~ company
  )) |>
  mutate(company = str_to_title(company)) |>
  mutate(company = str_replace(company, "Llc$", "LLC")) |>
  mutate(company = str_replace(company, " Of ", " of ")) |>
  count(company, sort = TRUE)
company_counts |>
  filter(n >= 2) |>
  ggplot(aes(x = n, y = reorder(company, n))) +
  geom_col(fill = "steelblue") +
  geom_text(aes(label = n), hjust = -0.3) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1))) +
  theme_minimal() +
  labs(title = "Disinformation Search Results",
       subtitle = "Articles Mentioning Business Disinformation",
       caption = "Graphic by Rob Wells, 9-15-2026",
       x = "Number of Articles",
       y = NULL)
```

#Count publications

```{r}
publication_counts <- data |>
  count(publication_4, sort = TRUE)
publication_counts
```


#Visualize publications

```{r}
publication_counts |>
  filter(n >= 3) |>
  mutate(publication_4 = case_when(
    str_detect(publication_4, "^Congressional Documents") ~ "Congressional Documents & Publications",
    str_detect(publication_4, "ANNALS") ~ "The ANNALS (American Academy of Political & Social Science)",
    TRUE ~ publication_4
  )) |>
  ggplot(aes(x = n, y = reorder(publication_4, n))) +
  geom_col(fill = "steelblue") +
  geom_text(aes(label = n), hjust = -0.3) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1))) +
  scale_y_discrete(labels = scales::label_wrap(30)) +
  theme_minimal() +
  labs(title = "Disinformation Search Results",
       subtitle = "Articles by Publication",
       caption = "Graphic by Rob Wells, 9-15-2026",
       x = "Number of Articles",
       y = NULL)
```




# NOTES ON FIXING COMPLEX Date COLUMN WITH HOURS AND MINUTES

```{r}
women <- women |> 
  mutate(date = as.Date(strptime(published_date, format = "%B %d, %Y %A")))
```